A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-28 01_background.Rmd

Releases of the package from Github can be found on Zenodo: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4033155.svg)](https://doi.org/10.5281/zenodo.4033155)

The build status of the 'Master' branch is shown here:

<!-- badges: start -->
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pratikunterwegs/atlastools?branch=master&svg=true)](https://ci.appveyor.com/project/pratikunterwegs/atlastools) 
  [![Build Status](https://travis-ci.org/pratikunterwegs/atlastools.svg?branch=master)](https://travis-ci.org/pratikunterwegs/atlastools) 
  [![codecov.io](https://codecov.io/github/pratikunterwegs/atlastools/coverage.svg?branch=master)](https://codecov.io/github/pratikunterwegs/atlastools/branch/master)
<!-- badges: end -->

>>>>

Releases of the package from Github can be found on Zenodo: (https://doi.org/10.5281/zenodo.4033155)

### 2020-10-28 06_bat_data.Rmd

```{r}
fig_bat_res_timeseries <-
  ggplot()+
  geom_path(data = data_residence,
            aes(ts, resTime,
                colour = TAG),
            show.legend = F)+
  scale_color_brewer(palette = "Dark2")+
  scale_x_datetime()+
  ggthemes::theme_few()+
  coord_cartesian(ylim = c(0, 50))+
  labs(x = NULL,
       y = "residence time (mins)")
```

>>>>

```{r}
fig_bat_res_timeseries <-
  ggplot()+
  geom_path(data = data_residence,
            aes(ts, resTime,
                colour = TAG),
            show.legend = F)+
  scale_color_brewer(palette = "Dark2")+
  scale_x_datetime()+
  ggthemes::theme_few()+
  labs(x = NULL,
       y = "residence time (mins)")
```
